Adaptive Test

### 2023-10-11 scripts/validation_ML_estimator.Rmd
add file
update ML validation description

After that, open an R IDE of your choice and install the required R packages with `renv::restore()`.
Please ensure to set the working directory to the `validate_ML_est` folder.

@@

The following plot shows the estimations errors when comparing our maximum likelihood estimation implementation with `catR`.

![](images/error_plot.png)

>>>>

After that, open an R IDE of your choice and install the required R packages with `renv::restore()`.
Please ensure to set the working directory to the `validate_ML_est` folder or simply open
the `cat_simulation.Rproj` file.

@@

Figure \@ref(fig:figs1) shows the distribution of estimation errors when comparing our maximum likelihood estimation implementation with `catR`. Differences between the two procedures are extremely small, all below 0.001.

```{r figs1}
library(ggplot2)
library(jsonlite)
library(ggthemes)

data <- as.numeric(jsonlite::read_json("../saves/estimation_errors.json"))
df <- data.frame(
  id = c(1:length(data)),
  error = data
)

ggplot(df, aes(x = error))+
  geom_density(fill = "grey", col = NA)+
  geom_jitter(aes(y = 0), pch = 1, width = 0.0001, alpha = 0.1, size =5)+
  xlim(-0.0015,0.0015)+
  labs(x = "Difference between Javascript and catR estimates", y = "Count")+
  theme_few()
